Playfair and the \"Flatten the Curve\" Graphic

### 2022-02-19 _posts/2022-02-19-playfair-and-the-flatten-the-curve-graphic/playfair-and-the-flatten-the-curve-graphic.Rmd
typo

As brilliant as the design was - far, far more effective than paragraphs of explanatory text with supporting tables of data - it was still a bit text-heavy, with two text axes and five chunks of (small) inline text that had to be read to fully understand its meaning, and similarly-colored curves showing the two different outcomes, so it wasn't quite a glance-level chart that could be instantly understood. When COVID-19 hit in 2019, this graphic was popularized and went through many iterations of further simplification, to makes its message as clear and impactful as possible. The New York Times published this version in 2020 [@robertsFlatteningCoronavirusCurve2020]:

>>>>

As brilliant as the design was - far, far more effective than paragraphs of explanatory text with supporting tables of data - it was still a bit text-heavy, with two text axes and five chunks of (small) inline text that had to be read to fully understand its meaning, and similarly-colored curves showing the two different outcomes, so it wasn't quite a glance-level chart that could be instantly understood. When COVID-19 hit in 2019, this graphic was popularized and went through many iterations of further simplification, to make its message as clear and impactful as possible. The New York Times published this version in 2020 [@robertsFlatteningCoronavirusCurve2020]:
